Apparent preferences for cognitive effort fade when multiple forms of effort

### 2021-04-15 Manuscript.Rmd
forgot one change in directory call

``` {r BTW and WTH: 16.3. Model fits, echo = FALSE, fig.align = "center", fig.width = 6, fig.height = 4}
## the fitting of these models was performed by a separate script (modeling_gk_btw/wth)
# here we load the results to economize computational power during knitting
# load results from models
load("Models/results/mod_results.Rdata")

>>>>

``` {r BTW and WTH: 16.3. Model fits, echo = FALSE, fig.align = "center", fig.width = 6, fig.height = 4}
## the fitting of these models was performed by a separate script (modeling_btw/wth)
# here we load the results to economize computational power during knitting
# load results from models
load("Models/results/mod_results.Rdata")
